### 2015-01-29 paper.tex
some truly horrible code

>>>>

Assume we have a fragment ``both houses and cars''.
The word \emph{both} has analyses \texttt{CoordConj} and
\texttt{Pron}, and \emph{houses} is ambiguous between \texttt{N} and \texttt{V}.
We have in our rule set the following rules:

\begin{enumerate}
\item remove N after Pron
\item select N after *Conj
\item select CoordConj before another CoordConj
\end{enumerate}

In the previous implementations, neither of rules 1 and 2 would fire
before we have disambiguated \emph{both} with rule 3.
In this implementation, we are creating all clauses before giving
them to the SAT solver. We express these constraints as implications:
\begin{itemize}
\item \emph{both} is \texttt{Pron} $\Rightarrow$ remove \texttt{N} for \emph{houses}
\item \emph{both} is \texttt{CoordConj} $\Rightarrow$ select
  \texttt{N} for \emph{houses}
\end{itemize}

For lemmas with only one reading, this leads to redundant clauses,
such as \texttt{Not (Var 8) :||: Not (Var 8)}, but SAT solver will
take care of them.
